%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Modified by Franklin Yu.

\documentclass[12pt, a4paper, roman]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates

% personal data
\name{Zhaolin}{Yu}
\title{Resumé}
\phone[mobile]{+1 (607) 768 0882}
\email{zyu13@binghamton.edu}
% \homepage{www.johndoe.com}                       % optional
\social[linkedin]{franklinyu}
\social[github]{franklinyu}
\social[twitter]{Franklin\_YZL}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle

\section{Education}
\cventry{2015--2016}{M.S. in Computer Science}{Binghamton University}{Binghamton}{\textit{3.87}}{}  % arguments 3 to 6 can be left empty
\cventry{2010--2014}{B.S. in Electric and Computer Engineering}{Shanghai Jiao Tong University}{Shanghai}{}{}

\section{Projects}
\cventry[1 em]{2016--now}{Solo project}{Votta}{}{}{
	A website for user to vote for their favorite thing, such as favorite kind of dog, favorite kind of text editor, or favorite kind of vegetable. Front-end based on Angular, back-end based on Rails.
}
\cventry[1 em]{2015 Jan.--now}{Contributor and Administrator}{Binghamton University Bike Share}{}{}{
	A website recording bike transactions and authenticate user during transactions. It records when a user takes or returns a bike, and decide whether to allow user to take the bike.
\\[1.5 ex]%
	In charge of:
	\begin{itemize}
		\item JSON API for hardware-team
		\item main architecture design
		\item Git repository
	\end{itemize}
}
\cventry[1 em]{2015 Fall}{Participant}{MIPS-like CPU Simulator}{}{}{
	Simulate an out-of-order CPU with instructions including arithmatics, memory operation and branching. Team of two.
}
\cventry{2014 Summer}{Participant}{Investication of Process Schedule Mechanism in Linux Kernel}{}{}{
	\begin{itemize}
	\item
		Implemented a pair of system call to switch on and off the process schedule recording.
	\item
		Implemented a simple process scheduling mechanism.
	\end{itemize}
}

\section{Languages and Tools}
\cvitem{Proficient}{Git, C/C++, Objective-C, Java, Ruby, GNU make}
\cvitem{Average}{Python, Shell and Linux CoreUtils, JavaScript, HTML/CSS}

\end{document}
